\chapter{Technical Coordination}
\label{ch:fdsp-coord}

Construction of the DUNE Far Detector is a very complex
activity. While the technology for massive noble liquid detectors has
developed over the last 45 years, the first large liquid Argon Time
Projection Chamber (LArTPC) was completed in 2010. While multiple
LArTPCs have operated worldwide, the technology is still relatively
new and the scale up to DUNE is significant.

DUNE consists of a large number of institutions distributed throughout
the world. They are supported by a large number of funding sources and
collaborate with a large number of commercial partners. DUNE has
empowered several Consortia (currently nine) with the responsibility
to secure funding for, design, fabricate, assemble, install,
commission and operate the key components of the DUNE far detector.

DUNE Technical Coordination, under the direction of the DUNE Technical
Coordinator, has responsibility to monitor the technical aspects of
the detector construction of the detector subsystems, to integrate the
detector and for a number of common projects. Groups of institutes
within DUNE form Consortia that take complete responsibility for
construction of their system.

Given the horizontal nature of the Consortia structure and the
extensive interdependencies between the systems, a significant
engineering organization is required to deliver DUNE on schedule and
within specifications and funding constraints.


\input{far-detector-single-phase/chapter-fdsp-coordination/support}
\input{far-detector-single-phase/chapter-fdsp-coordination/integration}
\input{far-detector-single-phase/chapter-fdsp-coordination/installation}

