%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Installation, Integration and Commissioning}
\label{sec:fdsp-pd-install}
%\todo{\color{blue} Content: Kemp}
%\metainfo{(Length: TDR=30 pages, TP=6 pages)}


%=================================================
\subsection{Transport and Handling}
\label{sec:fdsp-pd-install-transport}

Following assembly and testing of the PD modules they need to be carefully packaged and shipped to the far detector site for checkout and any final testing prior to installation into the cryostat. Handling and shipping procedures will depend on the environmental requirements determined for the photon detectors.

\begin{itemize}

\item Development of a testing plan to determine environmental requirements for photon detector handling and shipping. The environmental conditions apply for both surface and underground transport, storage and handling. Requirements for light (UV filtered areas), temperature, and humidity exposure should be developed.

\item Handling procedures need to be developed to ensure environmental requirements are met. This should include handling at all stages of component and system production and assembly, testing, shipping, and storage. It is likely that PD modules and components will be stored for periods of time during production and prior to installation into the FD cryostats. Appropriate storage facilities need to be constructed at locations where storage will take place.
\item Shipping and storage containers need to be designed and produced. Given the large number of photon detector modules to be installed in the FD, it will be advantageous to develop shipping containers that can be re-used.

\item Documentation and tracking of all components and PD modules will be required during the full production and installation schedule. Well defined procedures need to be in place to ensure that all components/modules are tested and examined prior to, and after, shipping. Information coming from such testing and examinations will be stored in a hardware database.

\item It is expected that photon detector will be assembled at more than one location and that components will come from a number of other locations. Oversight of the shipping and handling procedures will be critical. This responsibility should fall to a single institution and manager.

\item Integration and Test Facility (ITF) Operations:

	\begin{itemize}
	\item Transportation to and from ITF should be planned. The PDS units will be shipped from the production area in 	
	quantities compatible with the APA transport rates.   
	\item Operations: The PDS deliveries will be stored in temperature and humidity controlled storage area. Their mechanical 
	status will be inspected.
	\end{itemize}

\item Transportation to SURF: The delivery to SURF will be such that the storage time before integration will be at most two weeks.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Integration with APA}
\label{sec:fdsp-pd-install-pd-apa}

%\begin{itemize}

\subsubsection{Integration}
If the PDS detectors can be installed after the wire winding is completed, as in the present baseline design, their integration on the APA frame will happen at the Integration facility. Experts from both groups will work with the installation team. 
An electrical test with APA/PDS/CE will be performed at the integration facility in a cold box, after the integration of PDS and CE on the APA frame has been completed.

\subsubsection{Installation}
The APA consortium will be responsible for the transportation of the integrated APA frames from the integration facility to the LBNF/SURF facility. 
The UIT team, under supervision of the APA group, will be responsible to move the equipment into the clean room. 
Work on the 2-APA connection and inspection in the toaster is performed by the APA group.
Work on cabling in the toaster is performed by PDS and CE groups under supervision of the APA group.
Once the APAs will be moved inside the cryostat, the PDS and CE consortia will be responsible for the routing of the cables in the trays hanging from the top of the cryostat. 

%\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\color{red}\bf Installation into Cryostat and Cabling}
\label{sec:fdsp-pd-install-pd-cryo}
\fixme{\color{red} Kemp: Needs text.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Calibration/Monitoring}
\label{sec:fdsp-pd-install-calib}

The calibration and monitoring systems for the photon detector system will interface with several groups within the DUNE FD project, including the calibration group, slow controls group, and data acquisition group.

\begin{itemize}
\item The number of penetrations required for the calibration and monitoring systems need to be determined so that the cryostat design, including feedthroughs can be finalized.
\item Mounting requirements for the calibration system inside the cryostat need to be determined. Any light delivery hardware to be mounted on the cathode plane assemblies will need to be developed in coordination with the CPA group. A plan for fiber routing will need to be made. Cable routing and power distribution plans for both the calibration and monitoring
\item Readout of both the calibration and monitoring systems will need to be developed with the DAQ and slow controls groups. Mappings of the systems will need to be reflected in the PD hardware database.
\item Any calibration systems utilizing radioactive sources will need to be developed in coordination with the radiopurity and physics groups. It is important to ensure in addition, that any components of such a system do not contaminate the LAr or compromise the electron lifetime.
\end{itemize}
 


